Rapid cycleway prioritisation tool

### 2020-05-30 code/index.Rmd
Remove isles of scilly

```{r}
dn = "popupCycleways/v0.3" # dirctory name
built_regions = list.files(dn)
regions %>%
  sf::st_drop_geometry() %>%
  filter(html_name %in% built_regions) %>% 
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```

>>>>

```{r}
dn = "popupCycleways/v0.3" # dirctory name
built_regions = list.files(dn)
regions = regions %>% 
  filter(stringr::str_detect(string = Name, "Scilly", negate = TRUE))
regions %>%
  sf::st_drop_geometry() %>%
  filter(html_name %in% built_regions) 
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```
